---
title: "index"
author: "Mariah S., Ryan L., Shane F., Sumeet W."
date: "5/15/2020"
output: html_document
---

```{r setup, include=FALSE}
library("ggplot2")
library("dplyr")
library("tidyr")
library("plotly")
library("knitr")
#source("scripts/load_data.R")
source("scripts/summary.R")
source("scripts/summary_table.R")
#source("scripts/chart1.R")
source("scripts/chart2.R")
source("scripts/chart3.R")
# Edit load_data.R to load your data properly, then we all share the loaded
# datasets
```

During the strange and uncertain times we are currently living in, our group thought it fitting to use data related to the COVID-19 outbreak and try to understand how it has impacted (directly or indirectly) people around the world. Due to the stay-at-home orders issued around the world, many people find themselves at home for much longer than usual. We are collecting data on **Energy Usage**, **Mobility Trends**, and **Death Rates**. We will unpack these data sets to analyze both the environmental impact that COVID-19 (and the following human behavior) had, and the excess deaths beyond those attributed to COVID-19. By studying these data sets, we hope to learn more about how the COVID-19 outbreak has impacted the world beyond just how many are sick or dead because of the virus.

``` {r Summary_Table, echo = FALSE}
kable(aggregated_table(mobility), col.names = c("State", "Workplace", "Parks", "Grocery", "Retail", "Transit"))
```

```{r plot1, echo=FALSE}
# plot_1(mobility)
```

```{r plot2, echo=FALSE}
# plot_2(deaths)
```

```{r plot3, echo=FALSE}
plot_3(aggregated_table)
```